The Hyperedge Event Model

### 2018-05-28 paper/ba-HEM/ba-sample.tex
minor updates on the plots

	We evaluate the model's ability to predict edges and timestamps from Montgomery County email data, conditioned on their ``training" part of the data. To perform the experiment, we separately formed a test split of each three model components---sender, receivers, and timestamps---by randomly selecting ``test" data with probability $p=0.1$. Any missing variables were imputed by drawing samples from their conditional posterior distributions, given the observed data, model estimates, and current values of test data. We then run inference to update the latent variables given the imputed and observed data. We iterate the two steps---imputation and inference---multiple times to obtain enough number of estimates for test data. Algorithm \ref{alg:PPE} outlines this procedure in detail. We run the experiment and measure the predictive performance of two separate time distributions using $N=500$ predicted samples, by comparing the predictions in terms of classification accuracy in predicting the senders and receivers, as well as prediction error in the timestamps. We summarize the results of prediction experiments for missing senders, receivers, and timestamps in Figure \ref{figure:PPEresults}. First, we compare the posterior probability of correct senders for each of missing emails $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{obs}_{d}|\cdot)$ in Algorithm \ref{alg:PPE}. We call this measure as ``correct sender posterior probability." On Figure \ref{figure:PPEresults} (a), we draw boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{a_{d}} = \frac{1}{N}\sum_{n=1}^N \pi^n_{a_{d}}$---across the missing emails. The results show that both log-normal and exponential distributions acheive better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $A$ possible senders $=1/18$), with log-normal distribution showing slightly higher performance than exponential distribution on average. Secondly, since the receiver vector is binary, we compute $F_1$ scores for missing receiver indicators (i.e., all $d$ and $r$ with $r_{dr}$=NA) by taking the harmonic mean of precision and recall:

@@

	with TP denoting true positive (i.e., $\boldsymbol{r}^{obs}_{dr}=\boldsymbol{r}^{pred}_{dr}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{obs}_{dr}=1$ but $\boldsymbol{r}^{pred}_{dr}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{obs}_{dr}=0$ but $\boldsymbol{r}^{pred}_{dr}=1$). Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, Figure \ref{figure:PPEresults} (b) reveals noticeable difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal outperforms exponential. Finally, the prediction error for $d^{th}$ missing timestamp is estimated using the median of absolute relative errors\footnote{\cite{hyndman2006another} refer to this as median absolute percentage error (MdAPE).} across $N=500$ predictions:

>>>>

	We evaluate the model's ability to predict edges and timestamps from Montgomery County email data, conditioned on their ``training" part of the data. To perform the experiment, we separately formed a test split of each three model components---sender, receivers, and timestamps---by randomly selecting ``test" data with probability $p=0.1$. Any missing variables were imputed by drawing samples from their conditional posterior distributions, given the observed data, model estimates, and current values of test data. We then run inference to update the latent variables given the imputed and observed data. We iterate the two steps---imputation and inference---multiple times to obtain enough number of estimates for test data. Algorithm \ref{alg:PPE} outlines this procedure in detail. We run the experiment and measure the predictive performance of two separate time distributions using $N=500$ predicted samples, by comparing the predictions in terms of classification accuracy in predicting the senders and receivers, as well as prediction error in the timestamps. We summarize the results of prediction experiments for missing senders, receivers, and timestamps in Figure \ref{figure:PPEresults}. First, we compare the posterior probability of correct senders for each of missing emails $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{obs}_{d}|\cdot)$ in Algorithm \ref{alg:PPE}. We call this measure as ``correct sender posterior probability." On Figure \ref{figure:PPEresults} (a), we draw boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{a_{d}} = \frac{1}{N}\sum_{n=1}^N \pi^n_{a_{d}}$---across the missing emails. The results show that both log-normal and exponential distributions acheive better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $A$ possible senders $=1/18$), with log-normal distribution showing higher performance than exponential distribution. Secondly, since the receiver vector is binary, we compute $F_1$ scores for missing receiver indicators (i.e., all $d$ and $r$ with $r_{dr}$=NA) by taking the harmonic mean of precision and recall:

@@

	with TP denoting true positive (i.e., $\boldsymbol{r}^{obs}_{dr}=\boldsymbol{r}^{pred}_{dr}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{obs}_{dr}=1$ but $\boldsymbol{r}^{pred}_{dr}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{obs}_{dr}=0$ but $\boldsymbol{r}^{pred}_{dr}=1$). Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, Figure \ref{figure:PPEresults} (b) reveals slight difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal on average outperforms exponential. Finally, the prediction error for $d^{th}$ missing timestamp is estimated using the median of absolute relative errors\footnote{\cite{hyndman2006another} refer to this as median absolute percentage error (MdAPE).} across $N=500$ predictions:
